NCAM Explorer

### 2019-09-10 inst/rmd/vis_fit.Rmd
Update NCAM dashboard and include Comps and Projection tabs this time

```{r setup, echo=FALSE}
library(plotly)
library(Matrix)
library(knitr)
library(data.table)
library(webshot)
knitr::opts_knit$set(root.dir = tmp$output_dir)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

@@

cols <- viridis::viridis(4)[-1]
cols_rgb <-  paste0("rgb(", apply(col2rgb(cols), 2, paste, collapse = ","), ")")
fit <- tmp$fit # temp object from vis_fit function
if (!is.null(tmp$comp)) { comp <- tmp$comp }
if (!is.null(tmp$last)) { last <- tmp$last }
est <- as.list(fit$sd.rep, "Est")
sd <- as.list(fit$sd.rep, "Std")
tabs <- tidy_model(fit)
if (!is.null(tmp$comp)) { comp_tabs <- tidy_model(model_list = comp) }
if (!is.null(tmp$last)) { last_tabs <- tidy_model(tmp$last) }
if (!is.null(fit$retro)) { retro_tabs <- tidy_retro(fit) } 
min_year <- min(fit$tmb.data$years)
max_year <- max(fit$tmb.data$years)
ages <- fit$tmb.data$ages
years <- fit$tmb.data$years
years_plus1 <- fit$tmb.data$years_plus1

@@

@@

### Observed and predicted catch at age

@@

d <- tidy_mats(list(obs = fit$tmb.data$catch_prop,
                    pred = fit$rep$pred_prop_catch),
               ages = ages, years = years)
facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Proportion",
               obs_col = cols[2], pred_col = cols[1]) %>%
  layout(yaxis = list(rangemode = "tozero"))

@@

@@

### Catch at age surface (proportion)

@@

<!-- ### Catch at age surface (numbers) -->

<!-- ```{r} -->
<!-- plot_surface(mat = t(inputs$catch.num), ages = ages, years = years, name = "N") -->
<!-- ``` -->

<!-- > Note: model fits to composition - this plot is included for illustration -->

RV Survey
================================================================================

@@

d <- tidy_mats(list(obs = fit$tmb.data$RV_index,
                    pred = exp(fit$rep$Elog_RV_index),
                    wt = fit$tmb.data$est_wt),
               ages = ages, years = years)
d$obs[d$wt == 0] <- NA
d$pred[d$wt == 0] <- NA
facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Mean numbers per tow",
               obs_col = cols[2], pred_col = cols[1], type = "log")

@@

@@

SN Survey
================================================================================

@@

d <- tidy_mats(list(obs = fit$tmb.data$SN_GN_index,
                    pred = exp(fit$rep$Elog_SN_GN_index)),
               ages = fit$tmb.data$SN_ages, years = fit$tmb.data$SN_years)
facet_obs_pred(d, by = "age",
               which = c(3, 7, 4, 8, 5, 9, 6, 10), # done to order by column
               nrows = 4, ylab = "Sentinel survey index",
               obs_col = cols[2], pred_col = cols[1], type = "log")

@@

@@

SS Survey
================================================================================

@@

## Share data across multiple plots
d <- crosstalk::SharedData$new(tag_dat, ~exp, "Select an experiment")
base <- plot_ly(d, symbol = ~period, colors = cols[1:2], symbols = c(16, 1)) %>% group_by(exp)

@@

rel_plot <- base %>%
  filter(rel_year == cap_year) %>%
  group_by(exp) %>%
  summarise(rel_year = unique(rel_year), tot_rel = sum(n_rel), period = unique(period)) %>%
  add_markers(x = ~rel_year, y = ~sqrt(tot_rel), color = I(cols[1]),
              text = ~paste("exp:", exp, "</br>", "N:", tot_rel)) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = 0, y1 = 1000, yref = "y",
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "N released",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

@@

<!-- ### Animation -->

<!-- ```{r} -->

<!-- sum_d <- tag_dat %>% -->
<!--   group_by(exp, cap_year) %>% -->
<!--   summarise(sum_pred = sum(pred), sum_obs = sum(obs)) -->

<!-- sum_d %>%  -->
<!--   group_by(exp) %>%  -->
<!--   plot_ly(x = ~cap_year, frame = ~exp) %>% -->
<!--   add_markers(y = ~sqrt(sum_obs), color = I(cols[1]), name = "Observed", -->
<!--               text = ~paste("exp:", exp, "</br>", "observed N:", sum_obs)) %>% -->
<!--   add_lines(y = ~sqrt(sum_pred), color = I(cols[2]), name = "Predicted", -->
<!--             text = ~paste("exp:", exp, "</br>", "predicted N:", round(sum_pred))) %>% -->
<!--   animation_opts(1000, transition = 500, easing = "exp", redraw = FALSE) %>% -->
<!--   layout(yaxis = list(title = "N recaptured", -->
<!--                       tickvals = y_tickvals, -->
<!--                       ticktext = y_ticktext, -->
<!--                       range = range(y_tickvals)), -->
<!--          xaxis = list(title = "Year")) -->

<!-- ``` -->

@@

base %>%
  distinct(rel_year, Udev, exp, period) %>%
  add_markers(x = ~rel_year, y = ~Udev, text = ~exp, color = I(cols[1]),
              showlegend = FALSE) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = min(tag_dat$Udev), y1 = max(tag_dat$Udev),
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "Initial F deviation"),
         xaxis = list(title = "Year"))

@@

@@

pe <- fit$rep$pe
plot_surface(pe, years = c(years, fit$tmb.data$proj_years)[-1], ages = 2:8,
             name = "pe", col = RColorBrewer::brewer.pal(9, "RdBu")) %>%
  add_surface(matrix(0, nrow = nrow(pe), ncol = ncol(pe)), showscale = FALSE,
              color = I("black"), opacity = 0.8)

@@

```{r}
pe <- tidy_mat(fit$rep$pe, years = c(years, fit$tmb.data$proj_years)[-1],
               ages = 2:8, value = "res")
bubble_plot(pe)
```

@@

@@

@@

plot_xy_errorbar(sr, x = ~ssb_est, y = ~rec_est,
                 x_lwr = ~ssb_lwr, x_upr = ~ssb_upr,
                 y_lwr = ~rec_lwr, y_upr = ~rec_upr,
                 text = ~lab, xlab = "SSB (t)", ylab = "Recruitment",
                 col = cols[1])

@@

```{r}
p <- plot_xy_errorbar(sr, x = ~ssb_est, y = ~rps_est,
                 x_lwr = ~ssb_lwr, x_upr = ~ssb_upr,
                 y_lwr = ~rps_lwr, y_upr = ~rps_upr,
                 text = ~lab, xlab = "SSB (t)", ylab = "RPS (thousand / tonne)",
                 col = cols[1])
p
```

@@

@@

message("Bits of the projection code is currently not working. Specifically the plots that require the frame argument in plotly.")

@@

<!-- Assumptions  {data-navmenu="Projections" .storyboard} -->
<!-- ================================================================================ -->

<!-- ### Assume the same selectivity curve as estimated by NCAM in the terminal year and apply catch multipliers -->

<!-- ```{r} -->

<!-- Cp <- fit$tmb.data$Cp -->
<!-- Cp_string <- text_c(Cp) -->
<!-- Lp <- round(Cp * tail(fit$rep$pred_catch_wt, 1)) -->
<!-- Lp_string <- paste(text_c(Lp), "t") -->

<!-- tidy_mat(fit$rep$F_matrix, ages = ages, years = years, value = "F") %>% -->
<!--   filter(year >= max(years) - 4) %>% -->
<!--   plot_ly(x = ~age, y = ~F, color = ~factor(year), colors = rev(cols)) %>% -->
<!--   add_lines(alpha = 0.5) %>% -->
<!--   filter(year == max(years)) %>% -->
<!--   add_lines(showlegend = FALSE, line = list(width = 3)) %>% -->
<!--   layout(xaxis = list(title = "Age")) -->

<!-- ``` -->

<!-- *** -->
<!-- - The following catch multipliers were applied: `r #Cp_string` -->
<!-- - This translates to `r #Lp_string` of catch in the projection years -->

<!-- ### Assume natural mortality converges on the long-term mean, excluding the M spike between 1991 - 1994 -->

<!-- ```{r} -->

<!-- if (all(fit$tmb.data$Mp_mult != 1)) stop("TODO: make the mortality multiplier projection documentation dynamic") -->

<!-- aveM <- tabs$log_aveM -->
<!-- aveM <- exp(mean(aveM$est[!aveM$year %in% 1991:1994])) -->

<!-- trans_est(tabs$log_aveM) %>% -->
<!--   plot_trend(ylab = "Average M", col = cols[1]) %>% -->
<!--   add_segments(x = 1995, xend = max(years) + 3, y = aveM, yend = aveM, -->
<!--                name = "long-term mean", color = I("black"), line = list(width = 1)) %>% -->
<!--   add_segments(x = 1990, xend = 1995, y = aveM, yend = aveM, -->
<!--                name = "long-term mean", color = I("black"), -->
<!--                line = list(width = 1, dash = "dot")) %>% -->
<!--   add_segments(x = min(years), xend = 1990, y = aveM, yend = aveM, -->
<!--                name = "long-term mean", color = I("black"), line = list(width = 1)) %>% -->
<!--   add_text(x = max(years) + 0.2, y = aveM, text = "long-term mean", textposition = "bottom right", -->
<!--            color = I("black")) %>% -->
<!--   layout(xaxis = list(range = c(min(years), max(years) + 3))) -->

<!-- ``` -->

<!-- ### Assume a relationship between recruits per spawner and number of spawners to project recruits in the future -->

<!-- ```{r} -->

<!-- if (fit$tmb.data$Rp_mode != 3) stop("TODO: make the recruitment mode documentation dynamic") -->

<!-- rps_tab <- tabs$log_rps -->
<!-- names(rps_tab) <- c("year", "rps", "rps_sd", "rps_lwr", "rps_upr") -->
<!-- rps_tab <- rps_tab[rps_tab$year >= 1985, ] -->
<!-- rps_tab$year <- rps_tab$year - 2 # scale back two year to allign with spawners that produced the recruits -->
<!-- ssa_tab <- tabs$log_ssa -->
<!-- names(ssa_tab) <- c("year", "ssa", "ssa_sd", "ssa_lwr", "ssa_upr") -->
<!-- d <- merge(ssa_tab, rps_tab, by = "year") -->
<!-- rec_tab <- tabs$log_recruitment -->
<!-- names(rec_tab) <- c("year", "rec", "rec_sd", "rec_lwr", "rec_upr") -->
<!-- rec_tab <- rec_tab[rec_tab$year >= 1985, ] -->
<!-- rec_tab$year <- rec_tab$year - 2 # scale back two years -->
<!-- d <- merge(d, rec_tab, by = "year") -->
<!-- d$excluded <- d$year %in% 1991:1994 -->

<!-- sub_d <- d[!d$year %in% 1991:1994, ] -->
<!-- lin_rel <- lm(rps ~ ssa, data = sub_d) -->
<!-- # coefficients(lin_rel) -->

<!-- preds <- data.frame(year = NA, rps_sd = NA, ssa_sd = NA, ssa = seq(min(d$ssa), max(d$ssa), length.out = 100)) -->
<!-- preds$fits <- predict(lin_rel, newdata = preds) -->
<!-- preds$excluded <- FALSE -->

<!-- plot_ly(data = d, x = ~ssa, y = ~rps, text = ~year, -->
<!--         type = "scatter", mode = "markers", name = "est", -->
<!--         color = ~excluded, colors = c(cols[2], "grey"), -->
<!--         error_y = list(array = ~ qnorm(0.975) * rps_sd, -->
<!--                        width = 0, thickness = 1), -->
<!--         error_x = list(array = ~ qnorm(0.975) * ssa_sd, -->
<!--                        width = 0, thickness = 1)) %>% -->
<!--   add_text(text = ~year, textfont = list(color = toRGB("grey50")), textposition = "top right", -->
<!--            error_y = list(visible = FALSE), -->
<!--            error_x = list(visible = FALSE)) %>% -->
<!--   layout(title = "Spawners vs Recruits / Spawner", -->
<!--          xaxis = list(title = "log(Spawners)"), -->
<!--          yaxis = list(title = "log(Recruits / Spawner)", zerolinecolor = toRGB("lightgrey")), -->
<!--          showlegend = FALSE) %>% -->
<!--   add_lines(data = preds, x = ~ssa, y = ~fits, name = "fit", color = I(cols[1])) -->

<!-- ``` -->

<!-- *** -->
<!-- - Grey points indicate years excluded from the regressionn -->

<!-- ### Assume averages weights and proportions mature from the last three years -->

<!-- ```{r} -->

<!-- mat_p <- tidy_mat(fit$tmb.data$mat, ages = factor(ages), years = years, value = "mat") %>% -->
<!--   filter(year >= max(years) - 2) %>% -->
<!--   plot_ly(x = ~age, y = ~mat, color = ~factor(year), colors = rev(cols)) %>% -->
<!--   add_lines(alpha = 0.5) %>% -->
<!--   group_by(age) %>% -->
<!--   summarise(mat = mean(mat), year = "3y mean") %>% -->
<!--   add_lines(line = list(width = 3)) %>% -->
<!--   layout(xaxis = list(title = "Age"), -->
<!--          yaxis = list(title = "Proportion mature")) -->

>>>>

```{r setup, echo=FALSE}
library(plotly)
library(Matrix)
library(knitr)
library(data.table)
library(dplyr)
library(webshot)
knitr::opts_knit$set(root.dir = tmp$output_dir)
knitr::opts_chunk$set(echo = FALSE, fig.height = 7, fig.width = 8)
```

@@

cols <-  viridis::viridis(4)[c(2, 3, 1, 4)]
cols_rgb <-  paste0("rgb(", apply(col2rgb(cols), 2, paste, collapse = ","), ")")
fit <- tmp$fit # temp object from vis_fit function
if (!is.null(tmp$comp)) { comp <- tmp$comp }
if (!is.null(tmp$last)) { last <- tmp$last }
est <- as.list(fit$sd.rep, "Est")
sd <- as.list(fit$sd.rep, "Std")
tabs <- tidy_model(fit)
if (!is.null(tmp$comp)) { comp_tabs <- tidy_model(model_list = comp) }
if (!is.null(tmp$last)) { last_tabs <- tidy_model(tmp$last) }
if (!is.null(fit$retro)) { retro_tabs <- tidy_retro(fit) } 
min_year <- min(fit$tmb.data$years)
max_year <- max(fit$tmb.data$years)
ages <- fit$tmb.data$ages
years <- fit$tmb.data$years
years_plus1 <- fit$tmb.data$years_plus1

@@

### Numbers at age

d <- tidy_mats(list(obs = t(inputs$catch.num[as.character(years), as.character(ages)]),
                    pred = fit$rep$pred_catch),
               ages = ages, years = years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age", type = "log",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Proportion",
               obs_col = cols[2], pred_col = cols[1]) %>%
  layout(yaxis = list(rangemode = "tozero"))

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Predictions by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Numbers")
```

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Predictions by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = 1, end = 0.8),
              ylab = "Numbers")
```

> Y-axes in log scale; also note that model fits to composition - this plot is included for illustration

### Numbers at age surface

```{r}
plot_surface(mat = t(inputs$catch.num[as.character(years), as.character(ages)]), 
             ages = ages, years = years, name = "N")
```

> Note: model fits to composition - this plot is included for illustration

@@

### Proportions at age

@@

d <- tidy_mats(list(obs = fit$tmb.data$catch_prop,
                    pred = fit$rep$pred_prop_catch),
               ages = ages, years = years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Proportion",
               obs_col = cols[2], pred_col = cols[1]) %>%
  layout(yaxis = list(rangemode = "tozero"))

@@

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "linear", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Proportion", stack_group = TRUE)
```

> Note: values are stacked

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "linear", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = 1, end = 0.8),
              ylab = "Proportion", stack_group = TRUE)
```

> Note: values are stacked

@@

### Proportions at age surface

@@

RV Survey {data-navmenu="Surveys"}
================================================================================

@@

d <- tidy_mats(list(obs = fit$tmb.data$RV_index,
                    pred = exp(fit$rep$Elog_RV_index),
                    wt = fit$tmb.data$est_wt),
               ages = ages, years = years)
d$obs[d$wt == 0] <- NA
d$pred[d$wt == 0] <- NA
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(2, 8, 3, 9, 4, 10, 5, 11, 6, 12, 7, 13), # done to order by column
               nrows = 6, ylab = "Mean numbers per tow",
               obs_col = cols[2], pred_col = cols[1], type = "log")

@@

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Mean numbers per tow")
```

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE,
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = -1, end = 0.8),
              ylab = "Mean numbers per tow")
```

@@

SN Survey {data-navmenu="Surveys"}
================================================================================

@@

d <- tidy_mats(list(obs = fit$tmb.data$SN_GN_index,
                    pred = exp(fit$rep$Elog_SN_GN_index)),
               ages = fit$tmb.data$SN_ages, years = fit$tmb.data$SN_years)
d$cohort <- factor(d$year - d$age)
d$age <- factor(d$age)

facet_obs_pred(d, by = "age",
               which = c(3, 7, 4, 8, 5, 9, 6, 10), # done to order by column
               nrows = 4, ylab = "Sentinel survey index",
               obs_col = cols[2], pred_col = cols[1], type = "log")

@@

### Fits by age

```{r}
plot_obs_pred(data = d, showlegend = TRUE, 
              type = "log", group = "age",
              group_cols = viridis::viridis(nlevels(d$age), 
                                            direction = 1, end = 0.8),
              ylab = "Sentinel survey index")
```

### Fits by cohort

```{r}
plot_obs_pred(data = d, showlegend = TRUE,
              type = "log", group = "cohort",
              group_cols = viridis::viridis(nlevels(d$cohort), 
                                            direction = -1, end = 0.8),
              ylab = "Sentinel survey index")
```

@@

SS Survey {data-navmenu="Surveys"}
================================================================================

@@

## Share data across multiple plots
d <- crosstalk::SharedData$new(tag_dat, ~exp, "Select an experiment")
base <- plot_ly(d, symbol = ~period, colors = cols[1:2], symbols = c(16, 1)) %>% 
  group_by(exp) %>% 
  highlight(off = "plotly_relayout")

@@

rel_plot <- base %>%
  filter(rel_year == cap_year) %>%
  group_by(exp) %>%
  summarise(rel_year = unique(rel_year), tot_rel = sum(n_rel), period = unique(period)) %>%
  add_markers(x = ~jitter(rel_year, factor = 0.5), 
              y = ~sqrt(tot_rel), color = I(cols[1]),
              text = ~paste("exp:", exp, "</br>", "N:", tot_rel)) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = 0, y1 = 1000, yref = "y",
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "N released",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

@@

### Animation

sum_d <- tag_dat %>%
  group_by(exp, cap_year) %>%
  summarise(sum_pred = sum(pred), sum_obs = sum(obs))

sum_d %>%
  group_by(exp) %>%
  plot_ly(x = ~cap_year, frame = ~exp, hoverinfo = "x+y+text",
          showlegend = FALSE) %>%
  add_markers(y = ~sqrt(sum_obs), color = I(cols[1]),
              text = ~paste("exp:", exp, "</br>", "observed N:", sum_obs)) %>%
  add_lines(y = ~sqrt(sum_pred), color = I(cols[2]),
            text = ~paste("exp:", exp, "</br>", "predicted N:", round(sum_pred))) %>%
  animation_opts(1000, transition = 500, easing = "exp", redraw = FALSE) %>%
  layout(yaxis = list(title = "N recaptured",
                      tickvals = y_tickvals,
                      ticktext = y_ticktext,
                      range = range(y_tickvals)),
         xaxis = list(title = "Year"))

@@

base %>%
  filter(rel_year == cap_year) %>%
  add_markers(x = ~rel_year, y = ~Udev, text = ~exp, color = I(cols[1]),
              showlegend = FALSE) %>%
  layout(shapes = list(type = "line", x0 = 1996, x1 = 1996,
                       y0 = min(tag_dat$Udev), y1 = max(tag_dat$Udev),
                       line = list(width = 1, dash = "dot")),
         yaxis = list(title = "Initial F deviation"),
         xaxis = list(title = "Year"))

@@

<!-- ### Exploitable biomass at age -->

<!-- ```{r} -->
<!-- S <- apply(fit$rep$F_matrix, 2, function(x) x / max(x)) -->
<!-- B <- fit$rep$N_matrix[, seq(ncol(S))] * fit$tmb.data$midyw -->
<!-- E <- B * S -->
<!-- plot_surface(E, ages = ages, years = years, name = "Exploitable biomass") -->
<!-- ``` -->

@@

pe <- fit$rep$pe
plot_surface(pe, years = c(years, fit$tmb.data$proj_years)[-1], 
             ages = fit$tmb.data$pe_ages, name = "pe", 
             col = RColorBrewer::brewer.pal(9, "RdBu")) %>%
  add_surface(matrix(0, nrow = nrow(pe), ncol = ncol(pe)), showscale = FALSE,
              color = I("black"), opacity = 0.8)

@@

```{r}
pe <- tidy_mat(fit$rep$pe, years = c(years, fit$tmb.data$proj_years)[-1],
               ages = fit$tmb.data$pe_ages, value = "res")
bubble_plot(pe)
```

@@

### Mohn's rho

bms_plot <- trans_est(retro_tabs$log_ssb) %>%
  plot_mohns(col = cols[1], ylab = "SSB")

abn_plot <- trans_est(retro_tabs$log_recruitment, scale = 0.001) %>%
  plot_mohns(ylab = "Recruitment (age 2)", col = cols[1])

blim_plot <- trans_est(retro_tabs$log_ssb_lrp) %>%
  plot_mohns(ylab = "SSB/Blim", col = cols[1])

subplot(abn_plot, bms_plot, blim_plot, nrows = 3, shareX = TRUE, titleY = TRUE) %>% 
  layout(annotations = left_label("Relative difference", offset = 50),
         margin = list(l = 75))

> Relative difference = (retro estimate - current estimate) / current estimate; Mohn's rho = mean(relative difference)

### Difference

bms_plot <- retro_tabs$log_ssb %>%
  plot_retro_deltas(in_col = cols[1], ylab = "log(SSB)")

abn_plot <- retro_tabs$log_recruitment %>%
  plot_retro_deltas(ylab = "log(Recruitment)", in_col = cols[1])

blim_plot <- retro_tabs$log_ssb_lrp %>%
  plot_retro_deltas(ylab = "log(SSB/Blim)", in_col = cols[1])

subplot(abn_plot, bms_plot, blim_plot, nrows = 3, shareX = TRUE, titleY = TRUE) %>% 
  layout(annotations = left_label("Difference", offset = 50),
         margin = list(l = 75))

> Difference = retro estimate - current estimate; approximate 95% intervals based on retro standard deviation + current standard deviation

@@

### Mohn's rho

z_plot <- trans_est(retro_tabs$log_aveZ) %>%
  plot_mohns(ylab = "Average Z (ages 5+)", col = cols[1])

m_plot <- trans_est(retro_tabs$log_aveM) %>%
  plot_mohns(ylab = "Average M (ages 5+)", col = cols[1])

f_plot <- trans_est(retro_tabs$log_aveF) %>%
  plot_mohns(ylab = "Average F (ages 5+)", col = cols[1])

subplot(z_plot, m_plot, f_plot, nrows = 3, shareX = TRUE, titleY = TRUE) %>% 
  layout(annotations = left_label("Relative difference", offset = 50),
         margin = list(l = 75))

> Relative difference = (retro estimate - current estimate) / current estimate; Mohn's rho = mean(relative difference)

### Difference

z_plot <- retro_tabs$log_aveZ %>%
  plot_retro_deltas(ylab = "log(Average Z)", in_col = cols[1])

m_plot <- retro_tabs$log_aveM %>%
  plot_retro_deltas(ylab = "log(Average M)", in_col = cols[1])

f_plot <- retro_tabs$log_aveF %>%
  plot_retro_deltas(ylab = "log(Average F)", in_col = cols[1])

subplot(z_plot, m_plot, f_plot, nrows = 3, shareX = TRUE, titleY = TRUE) %>% 
  layout(annotations = left_label("Difference", offset = 50),
         margin = list(l = 75))

> Difference = retro estimate - current estimate; approximate 95% intervals based on retro standard deviation + current standard deviation

@@

plot_xy_errorbar(sr, x = ~ssb_est, y = ~rec_est,
                 x_lwr = ~ssb_lwr, x_upr = ~ssb_upr,
                 y_lwr = ~rec_lwr, y_upr = ~rec_upr,
                 text = ~lab, xlab = "SSB (t)", ylab = "Recruitment",
                 col = ~year, clab = "Year")

@@

```{r}
p <- plot_xy_errorbar(sr, x = ~ssb_est, y = ~rps_est,
                 x_lwr = ~ssb_lwr, x_upr = ~ssb_upr,
                 y_lwr = ~rps_lwr, y_upr = ~rps_upr,
                 text = ~lab, xlab = "SSB (t)", ylab = "RPS (thousand / tonne)",
                 col = ~year, clab = "Year")
p
```

@@

Assumptions  {data-navmenu="Projections" .storyboard}
================================================================================

### Assume the same selectivity curve as estimated by NCAM in the terminal year and apply catch multipliers

@@

Cp <- fit$tmb.data$Cp
Cp_string <- text_c(Cp)
Lp <- round(Cp * tail(fit$rep$pred_catch_wt, 1))
Lp_string <- paste(text_c(Lp), "t")

tidy_mat(fit$rep$F_matrix, ages = ages, years = years, value = "F") %>%
  filter(year >= max(years) - 4) %>%
  plot_ly(x = ~age, y = ~F, color = ~factor(year), colors = rev(cols)) %>%
  add_lines(alpha = 0.5) %>%
  filter(year == max(years)) %>%
  add_lines(showlegend = FALSE, line = list(width = 3)) %>%
  layout(xaxis = list(title = "Age"))

@@

***
- The following catch multipliers were applied: `r Cp_string`
- This translates to `r Lp_string` of catch in the projection years

### Assume natural mortality converges on the long-term mean, excluding the M spike between 1991 - 1994

if (all(fit$tmb.data$Mp_mult != 1)) stop("TODO: make the mortality multiplier projection documentation dynamic")

Mpe <- fit$rep$Mpe_matrix
Mproj <- replicate(fit$tmb.data$Yp, fit$tmb.data$pnm)
bpe <- fit$rep$bpe[, (fit$tmb.data$Y + 1):(fit$tmb.data$Y + fit$tmb.data$Yp)]
Mproj <- Mproj * exp(bpe)
Mproj <- cbind(Mpe, Mproj)
proj_years <- fit$tmb.data$proj_years

plot_surface(mat = Mproj, ages = ages, years = c(years, proj_years), name = "M")

### Assume mean recruitment from the last three years

last_three <- tail(fit$tmb.data$years, 3)
mean_rec <- exp(mean(tabs$log_recruitment$est[tabs$log_recruitment$year %in% last_three]))
mean_rec <- data.frame(year = c(last_three, last_three[3] + fit$tmb.data$Yp), 
                       mean_rec = mean_rec * 1000, grp = "mean")
trans_est(tabs$log_recruitment, scale = 0.001) %>%
  plot_trend(ylab = "Recruitment", col = cols[1]) %>% 
  add_lines(data = mean_rec, x = ~year, y = ~mean_rec, name = "mean",
            color = I("black"), line = list(width = 1)) %>% 
  add_text(x = max(years) + 1.2, y = mean_rec$mean_rec[1], 
           text = "mean recruitment", 
           textposition = "bottom right",
           color = I("black")) %>%
  layout(xaxis = list(range = c(min(years), max(years) + fit$tmb.data$Yp)))

### Assume averages weights and proportions mature from the last three years

mat_p <- tidy_mat(fit$tmb.data$mat, ages = factor(ages), years = years, value = "mat") %>%
  filter(year >= max(years) - 2) %>%
  plot_ly(x = ~age, y = ~mat, color = ~factor(year), colors = rev(cols)) %>%
  add_lines(alpha = 0.5) %>%
  group_by(age) %>%
  summarise(mat = mean(mat), year = "3y mean") %>%
  add_lines(line = list(width = 3)) %>%
  layout(xaxis = list(title = "Age"),
         yaxis = list(title = "Proportion mature"))

wt_p <- tidy_mat(fit$tmb.data$weight, ages = factor(ages), years = years, value = "weight") %>%
  filter(year >= max(years) - 2) %>%
  plot_ly(x = ~age, y = ~weight, color = ~factor(year), colors = rev(cols),
          showlegend = FALSE) %>%
  add_lines(alpha = 0.5) %>%
  group_by(age) %>%
  summarise(weight = mean(weight), year = "3y mean") %>%
  add_lines(line = list(width = 3)) %>%
  layout(xaxis = list(title = "Age"),
         yaxis = list(title = "Weight (kg)"))

subplot(mat_p, wt_p, titleY = TRUE, titleX = TRUE)

Past projections {data-navmenu="Projections" `r if (is.null(tmp$last)) ".hidden"`}
================================================================================

### Catch multiplier projections for SSB / Blim from the last RAP

```{r, eval = !is.null(tmp$last)}

d <- trans_est(last_tabs$Cproj_log_ssb_lrp)
d$scenario <- factor(d$scenario)
d$type <- "Projected"

past_d <- trans_est(last_tabs$log_ssb_lrp)
past_d <- past_d[past_d$year != max(past_d$year), ] # drop the last year here (it's in the projection output)
past_d <- lapply(levels(d$scenario), function(s) data.frame(past_d, scenario = s))
past_d <- do.call(rbind, past_d)
past_d$type <- "Estimated"
d <- rbind(past_d, d)
xlim <- c(max(last$tmb.data$years) - 5.1, max(years) + 1.1)
ylim <- range(d[d$year >= xlim[1] & d$year <= xlim[2], c("est", "lwr", "upr"), ])

current_d <- trans_est(tabs$log_ssb_lrp)
current_d <- lapply(levels(d$scenario), function(s) data.frame(current_d, scenario = s))
current_d <- do.call(rbind, current_d)
current_d$model <- "current RAP"
current_d$type <- "Estimated"
d$model <- "last RAP"
d <- rbind(d, current_d)

plot_proj(data = d, xlim = xlim, ylim = ylim, ylab = "SSB/Blim", group = "model",
          vline = max(last$tmb.data$years) + 1, hline = 1, col = cols, showlegend = TRUE,
          darken_proj = TRUE)

Retro projections {data-navmenu="Projections" `r if (is.null(fit$retro)) ".hidden"`}
================================================================================

### Catch multiplier projections for SSB / Blim from retrospective fits

d <- trans_est(retro_tabs$Cproj_log_ssb_lrp)
d$terminal_year <- as.numeric(as.character(d$terminal_year))
d$scenario <- factor(d$scenario)
d$type <- "Projected"

past_d <- trans_est(retro_tabs$log_ssb_lrp)
past_d$terminal_year <- as.numeric(as.character(past_d$terminal_year))
past_d <- past_d[past_d$year <= past_d$terminal_year, ] # drop the last year (it's in the projection output)
past_d <- lapply(levels(d$scenario), function(s) data.frame(past_d, scenario = s))
past_d <- do.call(rbind, past_d)
past_d$type <- "Estimated"
d <- rbind(past_d, d)
d <- d[order(d$scenario, d$terminal_year, d$year), ]

# xlim <- c(max(last$tmb.data$years) - 5.1, max(years) + 1.1)
# ylim <- range(d[d$year >= xlim[1] & d$year <= xlim[2], c("est", "lwr", "upr"), ])

plot_proj(data = d, ylab = "SSB/Blim", group = "terminal_year",
          hline = 1, col = rev(viridis::viridis(length(unique(d$terminal_year)))), 
          showlegend = TRUE, markers = FALSE, darken_proj = TRUE)

Results {data-navmenu="Projections"}
================================================================================

### Catch multiplier projections for SSB~yp~ / SSB~`r max(years) + 1`~

d <- trans_est(tabs$Cproj_log_ssb_ratio)
d[, c("est", "lwr", "upr")] <- (d[, c("est", "lwr", "upr")] - 1) * 100
d$scenario <- factor(d$scenario)
xlim <- c(max(years) + 0.9, max(years) + 4.1)
ylim <- range(d[d$year >= xlim[1] & d$year <= xlim[2], c("est", "lwr", "upr"), ])

plot_proj(data = d, xlim = xlim, ylim = ylim, ylab = "Percent growth", ticksuffix = "%",
          vline = max(years) + 1, col = cols[1]) %>%
  layout(yaxis = list(tickvals = seq(-200, 200, by = 25)))

### SSB / Blim

d <- trans_est(tabs$Cproj_log_ssb_lrp)
d <- d[d$year != max(years_plus1), ] # drop the first year (it's in the time series)
d$type <- "Projected"
d$scenario <- factor(d$scenario)

## Append full time series to projections
past_d <- trans_est(tabs$log_ssb_lrp)
past_d <- lapply(levels(d$scenario), function(s) data.frame(past_d, scenario = s))
past_d <- do.call(rbind, past_d)
past_d$type <- ifelse(past_d$year == max(years_plus1), "Projected", "Estimated")
d <- rbind(past_d, d)
xlim <- c(max(years) - 2.1, max(years) + 4.1)
ylim <- range(d[d$year >= xlim[1] & d$year <= xlim[2], c("est", "lwr", "upr"), ])
